% $Id: acknowledgements.tex,v 1.1 1997/10/19 19:35:59 davek Exp davek $
\begin{acknowledgements}
I would like to express my gratitude to my supervisor Maciej Koutny
for his patient support throughout the years it has taken me to
produce this thesis. He has been extraordinarily generous in finding time
for me, and his insistent probing of my ideas and rigorous attention
to detail have helped me immensely.  \\


Of course, I am indebted to the many researchers whose work is
mentioned in this thesis, but I would like to acknowledge a personal
debt to the following: Sergio Yovine and Stavros Tripakis for their
help with KRONOS and OPEN-KRONOS, respectively; Hubert Garavel for
support with CADP; and Gerard Holzmann and Jean-Charles
Gr{\'e}goire for sharing their code, from which I have learnt much
about efficient implementation.  \\


I have been fortunate to do this work surrounded by good friends and
colleagues. Chris Phillips gave me vital support during my
\mbox{M.Sc. studies} and has been a stalwart friend and adviser ever
since. Everyone in the High Integrity Embedded Systems Group has
provided friendly encouragement and contributed to a stimulating
environment in which to do research. Steven Bradley, William Henderson
and Adrian Robson have always been willing to listen to my ideas; they
are responsible for thrashing out much of the chaff. Ljerka Beus-Dukic
has never been short of an encouraging word, as I struggled through
the final stages of `writing up'. I consider myself particularly
fortunate to have shared an office with William Henderson for more
than a decade. He has been an unfailing source of good humour, good
music, good advice and good friendship. \\


I would like to thank the School of Computing and Mathematics at the
University of Northumbria, both for financial support and for the time which
it has allowed me to devote to this research. In this regard, I am
particularly grateful to Adrian Woolley for supporting my application for
a secondment to get the work started, and for managing my teaching allocation
sympathetically in subsequent years. \\


Above all others, I am grateful to Marilyn, my wife, best friend and
greatest ally, without whose loving support I would have given up long
ago, and to my children Caitlin, Martha and Josie, who always help to
keep things in perspective, and whose love makes everything seem
worthwhile.  \\
\end{acknowledgements}
